\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{PrimaryColor}{HTML}{004C8A}
\definecolor{SecondaryColor}{HTML}{333333}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large\bfseries\color{PrimaryColor}
}{}{0em}{}[\color{PrimaryColor}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------HEADER-----------
\begin{center}
    {\Huge \textbf{\textcolor{PrimaryColor}{NGUYỄN ĐĂNG PHÚC LỢI}}} \\ \vspace{5pt}
    \small \textbf{\textcolor{SecondaryColor}{BACKEND SOFTWARE ENGINEER}} $|$ \small Date of birth: 11/09/1995 \\ \vspace{4pt}
    \small \raisebox{-0.1\height}{\textcolor{PrimaryColor}{\faPhone}}\ \href{tel:0962948982}{0962948982} ~
    \href{mailto:phucloi.dev@gmail.com}{\raisebox{-0.2\height}{\textcolor{PrimaryColor}{\faEnvelope}}\ phucloi.dev@gmail.com} ~
    \href{https://github.com/rubyhcm}{\raisebox{-0.2\height}{\textcolor{PrimaryColor}{\faGithub}}\ github.com/rubyhcm} ~
    \href{https://phucloi.dev/}{\raisebox{-0.2\height}{\textcolor{PrimaryColor}{\faGlobe}}\ phucloi.dev} ~
    \href{https://www.linkedin.com/in/devruby/}{\raisebox{-0.2\height}{\textcolor{PrimaryColor}{\faLinkedin}}\ linkedin.com/in/devruby}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Backend Software Engineer with 6+ years building scalable \textbf{gRPC-first microservices} and RESTful APIs using \textbf{Ruby on Rails} and \textbf{Go}. Experienced in \textbf{Clean Architecture}, \textbf{CQRS} and event-driven architectures — across international teams in Vietnam, Japan, and globally.}
\vspace{-5pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Primary Languages}{: Go, Ruby (Python familiar)} \\ \vspace{1pt}
     \textbf{Architecture \& Design}{: RESTful APIs, Microservices, Distributed Systems, Serverless} \\ \vspace{1pt}
     \textbf{Frameworks}{: gRPC, Fiber, Chi, Ruby on Rails} \\ \vspace{1pt}
     \textbf{Databases}{: PostgreSQL, MySQL, Redis} \\ \vspace{1pt}
     \textbf{Data Processing \& Message Queues}{: Apache Kafka, RabbitMQ, Sidekiq, Redis Pub/Sub} \\ \vspace{1pt}
     \textbf{Cloud \& DevOps}{: AWS, GCP, Azure, Docker, CI/CD pipelines, Git} \\ \vspace{1pt}
     \textbf{Auth \& Security}{: OAuth2/OIDC, JWT, SSO, eKYC, Security best practices} \\ \vspace{1pt}
     \textbf{Testing \& Observability}{: RSpec, Testify, Sentry, Grafana, GitHub Actions, CircleCI} \\ \vspace{1pt}
     \textbf{AI Tools}{: Claude, GitHub Copilot}
    }}
 \end{itemize}
\vspace{-5pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {TTC AGRIS}{Oct 2025 -- Present}
      {Software Engineer $|$ Go (gRPC), Fiber, PostgreSQL, Redis, RabbitMQ, ArgoCD, Azure DevOps}{}
      \resumeItemListStart
        \resumeItem{Architected and developed scalable backend microservices with \textbf{Go} and \textbf{gRPC}; designed and owned 3 core services serving \textbf{10,000+ users}.}
        \resumeItem{Built robust APIs and managed event-driven data processing pipelines; optimized system reliability integrating PostgreSQL, Redis, and RabbitMQ.}
        \resumeItem{Troubleshot production issues and maintained CI/CD pipelines via \textbf{ArgoCD} and GitOps on \textbf{Azure DevOps}.}
      \resumeItemListEnd
      \vspace{7pt}

    \resumeSubheading
      {VIETNAM SILICON}{Mar 2025 -- Oct 2025}
      {Software Engineer $|$ Go, PostgreSQL, Redis, S3, Docker, Grafana, Microservices}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented high-performance microservices architecture using \textbf{Go} and \textbf{PostgreSQL} to handle real-world traffic at scale.}
        \resumeItem{Built clean, well-documented RESTful APIs and collaborated asynchronously with a globally distributed team.}
        \resumeItem{Conducted code reviews, contributed to architectural decisions, and containerized applications using \textbf{Docker}.}
      \resumeItemListEnd
      \vspace{7pt}

    \resumeSubheading
      {ICD VIETNAM}{Sep 2023 -- Mar 2025}
      {Software Engineer $|$ Ruby on Rails, Go, MySQL, Redis, Sidekiq, RabbitMQ, GCP, CircleCI}{}
      \resumeItemListStart
        \resumeItem{Engineered server-side systems and third-party APIs for enterprise clients using \textbf{Ruby on Rails} and \textbf{Go}; designed robust relational database schemas.}
        \resumeItem{Developed asynchronous data processing frameworks using \textbf{Sidekiq} and \textbf{RabbitMQ}, optimizing high-throughput performance.}
        \resumeItem{Worked independently across time zones, configuring \textbf{CircleCI} pipelines and managing cloud infrastructure on \textbf{GCP}.}
      \resumeItemListEnd
      \vspace{7pt}

    \resumeSubheading
      {IPFS}{Feb 2021 -- Sep 2023}
      {Back-end Developer $|$ Ruby on Rails, PostgreSQL, Kafka, Redis, Sidekiq, WebSocket, Docker}{}
      \resumeItemListStart
        \resumeItem{Built and maintained robust \textbf{microservices} with Ruby on Rails, \textbf{Apache Kafka}, and WebSocket; designed multi-tenancy isolation via API gateway.}
        \resumeItem{Managed asynchronous job processing with Sidekiq, optimizing system scalability and monitoring production reliability.}
      \resumeItemListEnd
      \vspace{7pt}

    \resumeSubheading
      {FREELANCER --- REMOTE}{May 2020 -- Feb 2021}
      {Back-end Developer $|$ Ruby on Rails, MySQL, PostgreSQL, GCP, GitHub Actions, CircleCI}{}
      \resumeItemListStart
        \resumeItem{Delivered end-to-end backend solutions — database design, RESTful API development, and cloud deployment on GCP — with automated CI/CD pipelines.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Information Technology (VNU-HCM)}{2020 -- 2023}
      {Bachelor of Information Technology -- GPA: 8.5/10}{}
      \vspace{7pt}
    \resumeSubheading
      {HCM University of Technology and Education}{2013 -- 2017}
      {Bachelor of Mechanical Engineering -- GPA: 7.0/10}{}
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------KEY PROJECTS-----------
\section{Key Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{PARTNER GATEWAY SERVICE} (Dec 2025) $|$ \emph{Go (Fiber), PostgreSQL, RabbitMQ, gRPC Client} $|$ \emph{Solo}}{}
          \resumeItemListStart
            \resumeItem{Engineered an API gateway bridging external partner APIs with internal \textbf{gRPC microservices}, handling authentication, rate limiting, and request routing via \textbf{Fiber v2}.}
            \resumeItem{Integrated \textbf{RabbitMQ} for event-driven workflows and gRPC clients to downstream services for inter-service communication.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{CRONJOB SERVICE} (Nov 2025) $|$ \emph{Go (gRPC), PostgreSQL, Redis, gocron v2, RabbitMQ} $|$ \emph{2 members}}{}
          \resumeItemListStart
            \resumeItem{Built a centralized cronjob management service with \textbf{gocron v2} and \textbf{Redis distributed locking}, triggering jobs via \textbf{gRPC} and \textbf{HTTP webhooks} with retry logic and execution history.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{CENTRE AUTHEN SERVICE} (Oct 2025) $|$ \emph{Go (gRPC), PostgreSQL, Redis, JWT, eKYC, SSO} $|$ \emph{Solo}}{}
          \resumeItemListStart
            \resumeItem{Architected a centralized authentication and authorization service serving \textbf{10,000+ users}.}
            \resumeItem{Integrated \textbf{VNPT eKYC} for identity verification and \textbf{SSO with Microsoft Teams} (Azure OAuth).}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{NOTIFICATION SERVICE} (Mar 2025) $|$ \emph{Go (Chi), PostgreSQL, Redis, Kafka, Line, Twilio, SendGrid} $|$ \emph{2 members}}{}
          \resumeItemListStart
            \resumeItem{Engineered an event-driven notification platform supporting email, SMS, Line, SSE, and FCM delivery via \textbf{Kafka}-based async processing.}
            \resumeItem{Designed and implemented RESTful APIs with both scheduled and on-demand notification triggering.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{IAM SERVICE} (Mar 2025) $|$ \emph{Go (Chi), Ory Helm Charts, PostgreSQL, Kubernetes} $|$ \emph{2 members}}{}
          \resumeItemListStart
            \resumeItem{Implemented centralized authentication and authorization using the \textbf{Ory} stack.}
            \resumeItem{Deployed and configured Ory components via Helm charts in a Kubernetes environment.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{HUMAN RESOURCE MANAGEMENT} (Sep 2024) $|$ \emph{Go (Fiber), MySQL, Testify, GitHub, Jira} $|$ \emph{4 members}}{}
          \resumeItemListStart
            \resumeItem{Created a company-wide HR system for managing employee records, attendance, and operations.}
            \resumeItem{Designed MySQL schemas, implemented RESTful APIs, and wrote unit tests with \textbf{Testify}.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{MEDIA SERVICE} (May 2024) $|$ \emph{Ruby on Rails, MySQL, Redis, Sidekiq, Google Cloud Storage, Observe} $|$ \emph{3 members}}{}
          \resumeItemListStart
            \resumeItem{Developed a file management service enabling customers to upload and download images via \textbf{Google Cloud Storage} integration.}
            \resumeItem{Designed database schemas, implemented APIs, and monitored production with Observe.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{GARMENT DESIGN MANAGEMENT} (Dec 2023) $|$ \emph{Ruby on Rails, MySQL, Sidekiq, Redis, Sentry, Vue.js} $|$ \emph{4 members}}{}
          \resumeItemListStart
            \resumeItem{Developed a production management platform for garment manufacturing oversight with \textbf{Vue.js} front-end support.}
            \resumeItem{Designed relational schemas, implemented APIs, and configured async job processing with Sidekiq.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{CHAT SUPPORT SERVICE} (Feb 2023) $|$ \emph{Ruby on Rails, MongoDB, WebSocket, GitLab} $|$ \emph{3 members}}{}
          \resumeItemListStart
            \resumeItem{Implemented a real-time chat system enabling customers to interact with support assistants via \textbf{WebSocket}.}
            \resumeItem{Developed APIs and wrote unit tests.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{SOCIAL PROJECT} (Apr 2022) $|$ \emph{Ruby on Rails, MongoDB, Sidekiq, Redis, Sentry, GitLab} $|$ \emph{3 members}}{}
          \resumeItemListStart
            \resumeItem{Developed a social platform allowing users to create posts, write reviews, and react to content.}
            \resumeItem{Built APIs, managed async jobs with Sidekiq, and monitored reliability using Sentry.}
          \resumeItemListEnd
          \vspace{2pt}

      \resumeProjectHeading
          {\textbf{MY BLOG} (Mar 2021) $|$ \emph{\href{https://phucloi.dev/}{phucloi.dev}} $|$ \emph{Ruby on Rails MVC, MySQL, Docker, GitHub, CircleCI} $|$ \emph{Solo}}{}
          \resumeItemListStart
            \resumeItem{Designed, developed, and deployed a personal technical blog with automated \textbf{CI/CD} pipeline from scratch.}
            \resumeItem{Managed full architecture, infrastructure, and ongoing maintenance as the sole developer.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
